
\section{Projects}

% See full list of projects on \website{dcetin.me/projects}
% \vspace{1em}

\outerlist{
\entrybig[\textbullet]
{\link{https://github.com/hethsheth/COVID-19-India}{\textbf{Predicting COVID-19 in India using Machine Learning}}}{April 2021}
{}{} % no sub-line so decrease next context
\vspace{-1em}
\innerlist{
\entry{Compiled, cleaned and visualized data from 4 sources, and 25 different features to create the dataset}
\entry{Tested over 5 machine (LR, ARIMA, HMM) and deep learning (LSTM, Seq2Seq) models against the second wave of the disease.}
\entry{Analyzed the impact of 10\% reduction in mobility on the number of cases using Linear Regression.}
}
}

\outerlist{
\entrybig[\textbullet]
{\link{https://devpost.com/software/groundwav}{\textbf{Rasoee: What am I eating?}}}{August 2020}
{PyTorch Global Summer Hackathon 2020 Runner Up}{}

\innerlist{
\entry{Developed an Android application that can recognize over 300 varieties food, and give links to recipes using an API call.}
\entry{Fine-tuned a pre-trained model in PyTorch on the Food-101 dataset.}
\entry{Deployed the model on the Android framework using TorchScript.}
}
}

\outerlist{
\entrybig[\textbullet]
{\textbf{TwoFace: An newer, easier authentication system}}{November 2019}
{2nd Runner ups in Microsoft code.fun.do++}{}

\innerlist{
\entry{Built an Ionic + Loopback application that uses face-verification as its login component.}
\entry{Integrated the Microsoft FaceAPI into the application to recognize, save, and verify faces.}
}
}


% \begin{minipage}[t]{0.48\textwidth}

% \outerlist{

% \entrybig[\textbullet]
% {\link{https://github.com/dcetin/bert-adv-embed}{\textbf{bert-adv-embed}} (Python/Chainer, 2019)}{}
% {Adversarial perturbations on BERT word embeddings}{}

% }

% \end{minipage}
